Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-09-01 ms/ms08_figures.tex
ENH improved figures
ENH
ENH plots

    \begin{subfigure}[]{\textwidth}
        \includegraphics[width=\textwidth]{\floatRelativePath/plthtmp_disease_comorbidity_matrix.py/corr_inkscape.png}
    \end{subfigure}

@@

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_hist_100000.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{f}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_egene_etissue_corr.png}
    \end{subfigure}

@@

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/plt.png}
    \end{subfigure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 9: graphical conclusions
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!ht]
    \centering

    \begin{subfigure}[]{0.99\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{fig/model1.png}
    \end{subfigure}

>>>>

    \begin{subfigure}[]{0.65\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_perc_tophits_eqtl.py/loci_explained_perc.png}
    \end{subfigure}

    \begin{subfigure}[]{0.85\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthtmp_disease_comorbidity_matrix.py/corr_inkscape.png}
    \end{subfigure}

@@

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_gwas.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_egene.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{c}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/plthst_gwas_egene_etissue.py/hist_etissue.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{d}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_egene_etissue_corr.png}
    \end{subfigure}

    \begin{subfigure}[]{.49\textwidth}
        \textbf{e}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_pleiotropic_regions_cumsum.py/pltbar_regions_cumsum.png}
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{f}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/cmpt_pleiotropic_regions.py/100000/region_hist_100000.png}
    \end{subfigure}

@@

    \begin{subfigure}[]{.49\textwidth}
        \textbf{a}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/histplot.png}
        %
    \end{subfigure}
    %
    \begin{subfigure}[]{.49\textwidth}
        \textbf{b}
        \\
        \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/histplot.png}
    \end{subfigure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 9: graphical conclusions
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{figure}[!ht]
%    \centering
%
%    \begin{subfigure}[]{0.99\textwidth}
%        \textbf{a}
%        \\
%        \includegraphics[width=\textwidth]{fig/model1.png}
%    \end{subfigure}
%
%\end{figure}
